### 2024-02-13 paper/paper.qmd
Organized all the files and deleted unnecessary files.

---
title: "The Analysis of Pluralistic Ignorance of Married Men in Saudi Arabia on Women Working Outside of Home (WWOH) ^[Code and data are available at: ]"
author: 
  - Tracy Yang
  - Alex Sun
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

#install.packages("tidyverse")
#install.packages("here")
#install.packages("knitr")

library(here)
library(knitr)
library(tidyverse)
library(haven)
library(dplyr)
```

```{r}
#Acquiring cleaned data from output folder
wwoh_data <-
  read_csv(
    file = here("outputs/data/cleaned_data.csv"))
```
\newpage

# Introduction

You can and should cross-reference sections and sub-sections.

The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

```{r}
#| echo: false
#| label: tbl-sum
#| fig-cap: Summary Statistics on Saudi Arabian Men Participated in Survey on WWOH

summary_stats <- wwoh_data |>
  group_by(condition2) |>
  summarize(
    Observations = n(),
    Mean_age = mean(age, na.rm =TRUE),
    Mean_children = mean(children, na.rm = TRUE),
    Percent_college = sum(college_deg, na.rm = TRUE)/n()*100,
    Percent_employed = sum(employed_now, na.rm = TRUE)/n()*100,
  ) |>
  bind_rows()|>
  mutate(group = c("Control", "Treatment")) |>
  select(condition2, everything())

summary_stats |> kable()

summary_all <- wwoh_data |>
  summarize(
    Observations = n(),
    Mean_age = mean(age, na.rm =TRUE),
    Mean_children = mean(children, na.rm = TRUE),
    Percent_college = sum(college_deg, na.rm = TRUE)/n()*100,
    Percent_employed = sum(employed_now, na.rm = TRUE)/n()*100)

summary_all |> kable()

```

### 2024-02-13 scripts/00-simulate_data.R

@@ -1,0 +1,32 @@
+#### Preamble ####
+# Purpose: Simulates possible data of married men in Saudi Arabia on giving consent to their wife working outside of home as well as their speculation on others' opinions.
+# Author: Tracy Yang, Alex Sun
+# Date: 12 February 2024
+# Contact: ycart.yang@mail.utoronto.ca; boyalexsun@gmail.com
+# License: MIT
+# Pre-requisites: None
+
+
+#### Workspace setup ####
+library(tidyverse)
+
+#### Simulate data ####
+set.seed(11)
+
+age <- round(runif(500, min = 18, max = 35))
+consent_own <- c(1, 0)
+consent_spec <- c(0:29)
+educ <- c(1,0)
+
+simulated_data <- tibble(age, consent_self = sample(
+  consent_own, 500, replace = TRUE),
+  consent_speculation = sample(consent_spec, 500, replace = TRUE),
+  education = sample(educ, 500, replace = TRUE)
+  )
+
+#### Testing Simulated Data ####
+simulated_data$age |> max() == 35
+simulated_data$consent_self |> unique() |> length() == 2
+simulated_data$consent_speculation |> length() == 500
+simulated_data$education |> class() == "numeric"
+

### 2024-02-13 scripts/02-data_cleaning.R

@@ -1,0 +1,27 @@
+#### Preamble ####
+# Purpose: Cleans the downloaded Saudi Arabia survey data for married men on giving consent to wife working outside of home.
+# Author: Tracy Yang, Alex Sun
+# Date: 12 February 2024
+# Contact: ycart.yang@mail.utoronto.ca; boyalexsun@gmail.com
+# License: MIT
+# Pre-requisites: 01-download_data.R
+
+#### Workspace setup ####
+library(tidyverse)
+library(janitor)
+library(dplyr)
+library(haven)
+
+#### Clean data ####
+raw_data <- read_dta("inputs/data/01_main_exp_clean.dta")
+
+#taking out NA data from age variable as well as single men in the survey.
+cleaned_data <- raw_data |> clean_names() |> na.omit(age)|> mutate(
+  age_groups = case_when(
+  age <= 23 ~ 1,
+  age >= 30 ~ 3,
+  TRUE ~ 2)) |> filter(married == 1)
+
+
+#### Save data ####
+write_csv(cleaned_data, "outputs/data/cleaned_data.csv")

### 2024-02-13 paper/paper.qmd
Finished most of introduction

@@
 ---
-title: "The Analysis of Pluralistic Ignorance of Married Men in Saudi Arabia on Women Working Outside of Home (WWOH) ^[Code and data are available at: ]"
+title: "The Analysis of Pluralistic Ignorance of Married Men in Saudi Arabia on Women Working Outside of Home (WWOH) ^[Code and data are available at: https://github.com/YcartXin/Analysis-of-Men-in-Saudi-Arabia-on-WWOH]"
 author: 
@@
   - Alex Sun
-thanks: "Code and data are available at: LINK."
 date: today
@@
 abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
-format: pdf
+format: 
+  typst:
+    toc: true
 number-sections: true
@@
 ```{r}
+#| include: false
+#| warning: false
+#| message: false
+
 #Acquiring cleaned data from output folder
@@
   read_csv(
-    file = here("outputs/data/cleaned_data.csv"))
+    file = here("data/analysis_data/cleaned_data.csv"))
 ```
@@
 
-You can and should cross-reference sections and sub-sections.
+In the landscape marked by rapid socio-economic transformations, Saudi Arabia continues to grapple with the enduring issue of gender inequality, manifesting in various forms of discrimination and unbalanced treatments towards women.
+In spite of recent reforms targeted at enhancing women’s rights, such as allowing women to drive and easing guardianship laws, challenges continue to persist in employment opportunities, legal rights, and societal expectations.
+This system is deeply rooted in cultural norms and a conservative interpretation of Islamic law, which collectively hinder women’s participation in society and public life.
 
-The remainder of this paper is structured as follows. @sec-data....
+With the constantly changing political landscape of Saudi Arabia, it is essential to consider sentiment in regards to the increasing presence of women in society.
+While it is known that Saudi Arabia and many other middle-eastern countries fall behind progressive nations in terms of legal women rights, there is a void of information in regards to whether the social sentiment is changing.
+Bursztyn, Gonzalez, and Yanagizawa-Drott directly address this issue by investigating the opinions of married men in Saudi Arabia (Bursztyn).
+
+Pluralistic ignorance describes the misalignment between private and public beliefs ().
+In the context of the paper by Bursztyn et.al.
+(year), it illustrates the discrepancy between an individual’s private support for women working outside the home (WWOH) and their belief of public opposition.
+The above authors’ findings suggest that the vast majority of married men aged 18-35 underestimate societal support for female employment, despite private beliefs that align more with progressive values.
+This gap between private attitudes and perceived social expectations highlights the need for interventions that accurately communicate societal beliefs to bridge the divide (Bursztyn).
+
+This paper will reproduce Bursztyn, Gonzalez, and Yanagizawa-Drott’s findings, while applying a demographic focused lens to establish if certain variables such as age or education have a bearing on support for WWOH.
+In particular, our paper will replicate the following three research claims:
+
++ The vast majority of married men in Saudi Arabia privately support WWOH
++ The married men massively underestimate the level of support from other men in their communities
++ Correcting these beliefs about others’ feelings will affect their wives decisions to work.
+
+For this paper, our estimand is the difference between the married men's guess on how many people in their survey group support WWOH and the actual percentage of people in their group that support WWOH.
+
+The remainder of this paper is structured as follows.
+We will first describe our data sources in @sec-data (Data), followed by a description of the variables and methodologies utilized by the original paper in @sec-results (Results).
+We will then conduct a reproduction of certain figures and results to verify the original paper’s findings in the same section.
+Afterwards, we will summarize our results when compared to the original paper.
+We will additionally conduct an in-depth examination of how various demographics affect the support for WWOH.
+Lastly, in @sec-discussion (Discussion), we will discuss the findings from @sec-results (Results) in context.
 
 # Data {#sec-data}
+
+# Results {#sec-results}
 
@@
 ```
+
+Our results are summarized in @tbl-modelresults.
+
+# Discussion {#sec-discussion}
+
+## First discussion point {#sec-first-point}
+
+If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
+
+## Second discussion point
+
+## Third discussion point
+
+## Weaknesses and next steps
+
+Weaknesses and next steps should also be included.
+
+\newpage
+
+\appendix
+
+# Appendix {-}
+
+# Additional data details
+
+## Posterior predictive check
+
+## Diagnostics
+
+\newpage
+
+# References

### 2024-02-13 paper/paper.qmd
Progressing in Data and Results.

@@
 + The married men massively underestimate the level of support from other men in their communities
-+ Correcting these beliefs about others’ feelings will affect their wives decisions to work.
++ Correcting these beliefs about others’ feelings will affect the outcome of whether the married man's wife work.
 
 For this paper, our estimand is the difference between the married men's guess on how many people in their survey group support WWOH and the actual percentage of people in their group that support WWOH.
-
 The remainder of this paper is structured as follows.
@@
 
+## Data source and collection
+The data used in this analysis - Main Experiment of Saudi Arabia men on WWOH and their beliefs of others’ opinions  - is sourced from the replication package provided by Bursztyn et.al (year).
+The data was collected by the researchers in the original paper through an experiment and repeated surveys with a treatment group and a control group.
+This analysis will be carried out in R [6] using packages tidyverse [7], knitr [8], dplyr [9], ggplot2 [10], knitr [8], and here [11].
+Although the experiment claims to have only recruited men who are married, the data shows otherwise and thus some data points will be further removed from the analysis.
+The paper was published in the American Economic Review 2020, 110(10) issue between pages 2997-3029 ().
+The data was similarly uploaded at the same time and has not been updated since.
+
+More specifically, the sampling for the experiment was conducted through a partnership between a local branch of an international survey company and Bursztyn et.al.
+They recruited 500 Saudi Arabia men between the ages of 18 and 35, living across Riyadh, Saudi Arabia ().
+
 # Results {#sec-results}
+In this section, we will replicate some of the graphs, tables, and findings in the original paper.
+
+The data collected from the experiment can be introduced through summary statistics.
 
@@
     Observations = n(),
-    Mean_age = mean(age, na.rm =TRUE),
-    Mean_children = mean(children, na.rm = TRUE),
-    Percent_college = sum(college_deg, na.rm = TRUE)/n()*100,
-    Percent_employed = sum(employed_now, na.rm = TRUE)/n()*100)
+    Age = mean(age, na.rm =TRUE),
+    Children = mean(children, na.rm = TRUE),
+    "College" = sum(college_deg, na.rm = TRUE)/n()*100,
+    "Employed(%)" = sum(employed_now, na.rm = TRUE)/n()*100)
 
@@
 
-Our results are summarized in @tbl-modelresults.
+As seen in @tbl-sum above, there are less than 500 data points present after removing single men as well as any empty data points used in the making of the summary statistics, contrary to the claims of Bursztyn et.al.
 

### 2024-02-13 paper/paper.qmd
updated scripts and references

@@
 The data was collected by the researchers in the original paper through an experiment and repeated surveys with a treatment group and a control group.
-This analysis will be carried out in R [6] using packages tidyverse [7], knitr [8], dplyr [9], ggplot2 [10], knitr [8], and here [11].
+This analysis will be carried out in **R** @citeR using packages **tidyverse** @tidyverse, **knitr** @knitr, **dplyr** @dplyr, **ggplot2** @ggplot2, **knitr** @knitr, **here ** @here.
 Although the experiment claims to have only recruited men who are married, the data shows otherwise and thus some data points will be further removed from the analysis.
@@
 #| label: tbl-sum
-#| fig-cap: Summary Statistics on Saudi Arabian Men Participated in Survey on WWOH
+#| fig-cap: Summary Statistics on Men Who Participated in the Main Experiment
 
@@
     Observations = n(),
-    Mean_age = mean(age, na.rm =TRUE),
-    Mean_children = mean(children, na.rm = TRUE),
-    Percent_college = sum(college_deg, na.rm = TRUE)/n()*100,
-    Percent_employed = sum(employed_now, na.rm = TRUE)/n()*100,
+    Age = mean(age, na.rm =TRUE),
+    Children = mean(children, na.rm = TRUE),
+    "College(%" = sum(college_deg, na.rm = TRUE)/n()*100,
+    "Employed(%)" = sum(employed_now, na.rm = TRUE)/n()*100,
   ) |>
@@
 \newpage
-
-# References

### 2024-02-13 scripts/01-download_data.R

@@ -8,19 +8,20 @@
 # Any other information needed? [...UPDATE THIS...]
 
 
-#### Workspace setup ####
-library(opendatatoronto)
+#### Workspace setup ####)
 library(tidyverse)
+library(haven)
 # [...UPDATE THIS...]
 
 #### Download data ####
-# [...ADD CODE HERE TO DOWNLOAD...]
-
-
+raw_wwoh_data <-
+  read_dta(
+    file = "data/raw_data/01_main_exp_clean.dta"
+  )
 
 #### Save data ####
 # [...UPDATE THIS...]
 # change the_raw_data to whatever name you assigned when you downloaded it.
-write_csv(the_raw_data, "inputs/data/raw_data.csv") 
+#write_csv(the_raw_data, "data/raw_data/01_main_exp_clean.dta") 
 
          

### 2024-02-13 scripts/02-data_cleaning.R

@@ -13,7 +13,7 @@ library(dplyr)
 library(haven)
 
 #### Clean data ####
-raw_data <- read_dta("inputs/data/01_main_exp_clean.dta")
+raw_data <- read_dta("data/raw_data/01_main_exp_clean.dta")
 
 #taking out NA data from age variable as well as single men in the survey.
 cleaned_data <- raw_data |> clean_names() |> na.omit(age)|> mutate(
@@ -24,4 +24,4 @@ cleaned_data <- raw_data |> clean_names() |> na.omit(age)|> mutate(
 
 
 #### Save data ####
-write_csv(cleaned_data, "outputs/data/cleaned_data.csv")
+write_csv(cleaned_data, "data/analysis_data/cleaned_data.csv")

### 2024-02-13 paper/paper.qmd
Fixed Table 1 with captions and proper organization.

--- 2024-02-13 paper/paper.qmd
@@
 #install.packages("knitr")
+#install.packages("rmarkdown")
 
@@
 library(dplyr)
+library(rmarkdown)
 ```
@@
 ```
+
 \newpage
@@
 While it is known that Saudi Arabia and many other middle-eastern countries fall behind progressive nations in terms of legal women rights, there is a void of information in regards to whether the social sentiment is changing.
-Bursztyn, Gonzalez, and Yanagizawa-Drott directly address this issue by investigating the opinions of married men in Saudi Arabia (Bursztyn).
+Bursztyn, Gonzalez, and Yanagizawa-Drott directly address this issue by investigating the opinions of married men in Saudi Arabia @paper.
 
-Pluralistic ignorance describes the misalignment between private and public beliefs ().
+Pluralistic ignorance describes the misalignment between private and public beliefs XX.
 In the context of the paper by Bursztyn et.al.
-(year), it illustrates the discrepancy between an individual’s private support for women working outside the home (WWOH) and their belief of public opposition.
+(2020), it illustrates the discrepancy between an individual’s private support for women working outside the home (WWOH) and their belief of public opposition.
 The above authors’ findings suggest that the vast majority of married men aged 18-35 underestimate societal support for female employment, despite private beliefs that align more with progressive values.
-This gap between private attitudes and perceived social expectations highlights the need for interventions that accurately communicate societal beliefs to bridge the divide (Bursztyn).
+This gap between private attitudes and perceived social expectations highlights the need for interventions that accurately communicate societal beliefs to bridge the divide @paper.
 
@@
 ## Data source and collection
-The data used in this analysis - Main Experiment of Saudi Arabia men on WWOH and their beliefs of others’ opinions  - is sourced from the replication package provided by Bursztyn et.al (year).
+The data used in this analysis - Main Experiment of Saudi Arabia men on WWOH and their beliefs of others’ opinions  - is sourced from the replication package provided by Bursztyn et.al (2020).
 The data was collected by the researchers in the original paper through an experiment and repeated surveys with a treatment group and a control group.
-This analysis will be carried out in R [6] using packages tidyverse [7], knitr [8], dplyr [9], ggplot2 [10], knitr [8], and here [11].
+This analysis will be carried out in **R** @R using packages **tidyverse** @tidyverse, **dplyr** @dplyr, **ggplot2** @ggplot2, **knitr** @knitr, **here ** @here.
 Although the experiment claims to have only recruited men who are married, the data shows otherwise and thus some data points will be further removed from the analysis.
-The paper was published in the American Economic Review 2020, 110(10) issue between pages 2997-3029 ().
+The paper was published in the American Economic Review 2020, 110(10) issue between pages 2997-3029 @paper.
 The data was similarly uploaded at the same time and has not been updated since.
@@
 More specifically, the sampling for the experiment was conducted through a partnership between a local branch of an international survey company and Bursztyn et.al.
-They recruited 500 Saudi Arabia men between the ages of 18 and 35, living across Riyadh, Saudi Arabia ().
+They recruited 500 Saudi Arabia men between the ages of 18 and 35, living across Riyadh, Saudi Arabia @paper.
 
@@
 #| echo: false
-#| label: tbl-sum
-#| fig-cap: Summary Statistics on Saudi Arabian Men Participated in Survey on WWOH
-
+#| label: tbl-summ
+#| tbl-cap: Summary Statistics on Men Who Participated in the Main Experiment
 summary_stats <- wwoh_data |>
@@
     Observations = n(),
-    Mean_age = mean(age, na.rm =TRUE),
-    Mean_children = mean(children, na.rm = TRUE),
-    Percent_college = sum(college_deg, na.rm = TRUE)/n()*100,
-    Percent_employed = sum(employed_now, na.rm = TRUE)/n()*100,
+    Age = mean(age, na.rm =TRUE),
+    Children = mean(children, na.rm = TRUE),
+    "College(%" = sum(college_deg, na.rm = TRUE)/n()*100,
+    "Employed(%)" = sum(employed_now, na.rm = TRUE)/n()*100,
   ) |>
   bind_rows()|>
-  mutate(group = c("Control", "Treatment")) |>
-  select(condition2, everything())
+  mutate(group = c("Control", "Treatment"))
 
@@
   summarize(
-    Observations = n(),
+    Total = n(),
     Age = mean(age, na.rm =TRUE),
@@
 
-As seen in @tbl-sum above, there are less than 500 data points present after removing single men as well as any empty data points used in the making of the summary statistics, contrary to the claims of Bursztyn et.al.
+As seen in @tbl-summ above, there are less than 500 data points present after removing single men as well as any empty data points used in the making of the summary statistics, contrary to the claims of Bursztyn et.al.
+```{r}
+
+```
+
+```{r}
+#| echo: false
+#| label: fig-time
+#| fig-cap: Density Histogram of Percentage Wedge
+cleaned_data <- wwoh_data |>
+  mutate(percentage_wedge = outside_wedge/30*100)
+
+p <- ggplot(cleaned_data, aes(x = percentage_wedge)) + 
+  geom_histogram(aes(y = after_stat(density)), binwidth = 8, fill = "green", alpha = 0.6, color = "black") + 
+  labs(
+       x = "Percentage Wedge Value",
+       y = "Density",
+       caption = "Distribution of the difference between beliefs on what percentage people support WWOH and actual percentage of people that support WWOH.
+The values were calculated as (participants guess about percent of session participants that agree with WWOH - the actual percentage of participants that agree with WWOH") +
+  theme_minimal() +
+  theme(plot.caption = element_text(hjust = 0, face = "italic", size = 10),
+        plot.caption.position = "plot") +
+  scale_x_continuous(limits = c(-100, 100))
+
+print(p)
+```
+In @fig-time, we plotted the “wedge” between the participant’s belief in what percentage of others would support WWOH and how many participants actually supported WWOH.
+In assessing the distribution of these wedges throughout all sessions, the data revealed that a substantial majority (72%) of the participants consistently undervalue the level of endorsement for WWOH within their session cohorts.
+On average, this wedge is observed to be a 24 percentage points difference, aligning very similarly with the conclusions drawn from the original paper @paper.
 

### 2024-02-14 paper/paper.qmd
Deleted unnecessary folders and files; worked further on the data section.

@@
 #install.packages("knitr")
-#install.packages("rmarkdown")
 
@@
 library(dplyr)
-library(rmarkdown)
 ```
@@
 This analysis will be carried out in **R** @R using packages **tidyverse** @tidyverse, **dplyr** @dplyr, **ggplot2** @ggplot2, **knitr** @knitr, **here ** @here.
-Although the experiment claims to have only recruited men who are married, the data shows otherwise and thus some data points will be further removed from the analysis.
 The paper was published in the American Economic Review 2020, 110(10) issue between pages 2997-3029 @paper.
@@
 They recruited 500 Saudi Arabia men between the ages of 18 and 35, living across Riyadh, Saudi Arabia @paper.
+However, the data's sampling methodology also contains flaws.
+There is incongruity between what the paper claims the data to be and what the data shows.
+For example, although the experiment claims to have only recruited men who are married, the data shows otherwise and thus some data points will be further removed from the analysis.
+The participants' highest education also ranges from a secondary degree to a doctorate degree even though the original paper claims that they sampled with lowest some kind of college degree @paper.
+The secondary degree participants, however, will not be removed from the data set as they do not affect the purpose of the analysis, and further investigation on the effect of education on the support of WWOH will be conducted in @sec-results.
+The sample of 500 men with some removed due to empty data points and others due to attribute qualifications is quite small to be very representative of the male population in Saudi Arabia.
+The cleaned data will be further explored in @sec-explore.
+
+## Exploring the data {#sec-explore}
+After the data cleaning process, relevant variables are left
+
+## Measurement
 

### 2024-02-14 scripts/01-data_cleaning.R

@@ -4,7 +4,7 @@
 # Date: 12 February 2024
 # Contact: ycart.yang@mail.utoronto.ca; boyalexsun@gmail.com
 # License: MIT
-# Pre-requisites: 01-download_data.R
+# Pre-requisites: None
 
 #### Workspace setup ####
 library(tidyverse)

### 2024-02-14 scripts/01-download_data.R

@@ -1,27 +1,0 @@
-#### Preamble ####
-# Purpose: Downloads and saves the data from [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
-# License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
-
-
-#### Workspace setup ####)
-library(tidyverse)
-library(haven)
-# [...UPDATE THIS...]
-
-#### Download data ####
-raw_wwoh_data <-
-  read_dta(
-    file = "data/raw_data/01_main_exp_clean.dta"
-  )
-
-#### Save data ####
-# [...UPDATE THIS...]
-# change the_raw_data to whatever name you assigned when you downloaded it.
-#write_csv(the_raw_data, "data/raw_data/01_main_exp_clean.dta") 
-
-         

### 2024-02-14 paper/paper.qmd
Added new online national data set into scripts and paper; updated the Data section

@@
 #Acquiring cleaned data from output folder
+online_cleaned <-
+   read_csv(
+    file = here("data/analysis_data/online_cleaned.csv"))
 wwoh_data <-
   read_csv(
-    file = here("data/analysis_data/cleaned_data.csv"))
+    file = here("data/analysis_data/main_cleaned.csv"))
+
 ```
@@
 
-# Introduction
+# Introduction {#sec-intro}
 
@@
 
-## Data source and collection
-The data used in this analysis - Main Experiment of Saudi Arabia men on WWOH and their beliefs of others’ opinions  - is sourced from the replication package provided by Bursztyn et.al (2020).
-The data was collected by the researchers in the original paper through an experiment and repeated surveys with a treatment group and a control group.
+## Data source
 This analysis will be carried out in **R** @R using packages **tidyverse** @tidyverse, **dplyr** @dplyr, **ggplot2** @ggplot2, **knitr** @knitr, **here ** @here.
@@
 The data was similarly uploaded at the same time and has not been updated since.
+There are two data sets out of others collected in the original research that this paper will utilize.
 
-More specifically, the sampling for the experiment was conducted through a partnership between a local branch of an international survey company and Bursztyn et.al.
+The first data used in this analysis - "1st Online Survey Clean" - is sourced from the replication package provided by Bursztyn et.al (2020).
+The data was collected by the researchers in the original paper through an online survey with a treatment group and a control group.
+This imported data contains 1460 observations and 21 variables.
+
+The second data used in this analysis - "Main Experiment Clean" - is also sourced from the replication package provided by Bursztyn et.al (2020).
+The data was collected by the researchers in the original paper through a more selective filtering process with an experiment conducted in-person with a treatment group and a control group.
+This data contains 500 observations and 36 variables.
+
+## Measurement and collection
+The "1st Online Survey Clean" will only be used to conduct analysis on the support of married Saudi Arabian men on women working outside of home.
+Therefore, its selection process is not extremely extensive.
+The qualifying characteristics are marriage status (married) and age (18-35).
+This survey was conducted nationally and anonymously.
+The other aspects of this survey is not further discussed as the data will not be used in this paper.
+
+However, the main experiment data needs a more extensive examination.
+The sampling for the experiment was conducted through a partnership between a local branch of an international survey company and Bursztyn et.al.
 They recruited 500 Saudi Arabia men between the ages of 18 and 35, living across Riyadh, Saudi Arabia @paper.
-However, the data's sampling methodology also contains flaws.
+The requirement for the men to sampled includes being married, having a cell phone (for easy reach and communication), and having minimum some kind of college education @paper.
+All qualifying subjects were invited to a hotel to conduct the experiment portion in-person.
+The men were separated into groups of 30 with the average participant knowing 15 out of the 29 of other participants @paper.
+They were then surveyed on WWOH and whether they would support their wives working outside of home.
+The research team then reveals the opinions of other participants in the room and distributes another survey on whether the participants would support their wives working outside of home.
+
+Even though the data imported has already been cleaned, it is not in the state that can be directly used in this paper.
+The cleaning process will keep XX as they are relevant to replicate the targeted aspects and the following analysis.
+Additionally, the main experiment's raw data's sampling methodology also contains flaws.
 There is incongruity between what the paper claims the data to be and what the data shows.
 For example, although the experiment claims to have only recruited men who are married, the data shows otherwise and thus some data points will be further removed from the analysis.
-The participants' highest education also ranges from a secondary degree to a doctorate degree even though the original paper claims that they sampled with lowest some kind of college degree @paper.
+The participants' highest education also ranges from a secondary degree to a doctorate degree even though the original paper claims that they sampled men with lowest college degree @paper.
 The secondary degree participants, however, will not be removed from the data set as they do not affect the purpose of the analysis, and further investigation on the effect of education on the support of WWOH will be conducted in @sec-results.
@@
 ## Exploring the data {#sec-explore}
-After the data cleaning process, relevant variables are left
+After the data cleaning process, irrelevant variables were removed along with empty responses.
+The online survey data now consists of only one variable with 728 observations.
+The variable signifies whether the respondent supports women working outside of home.
 
-## Measurement
+@tbl-sampleonline shows what the online national survey data looks like after cleaning.
+
+```{r}
+#| echo: false
+#| label: tbl-sampleonline
+#| tbl-cap: Sample of Cleaned Online National Survey Data of Saudi Arabian Men on WWOH
+online_cleaned |> slice(1:5) |> kable()
+
+```
+
+For the cleaned main experiment data, irrelevant variables and empty responses were also deleted. It now consists of XX observations with XX variables. 
+The variables are listed and explained below:
+
+@tbl-samplemain shows what the cleaned data for the main experiment looks like.
+```{r}
+#| echo: false
+#| label: tbl-samplemain
+#| tbl-cap: Sample of Cleaned Main Experiment Data of Saudi Arabian Men on WWOH
+wwoh_data |> slice(1:5) |> kable()
+
+```
 
 # Results {#sec-results}
-In this section, we will replicate some of the graphs, tables, and findings in the original paper.
+This section will first affirm the findings in the original paper with the cleaned data. As stated in @sec-intro, the three main claims made by Bursztyn et.al are:
++ The vast majority of married men in Saudi Arabia privately support WWOH.
++ The married men massively underestimate the level of support from other men in their communities.
++ Correcting these beliefs about others’ feelings will affect the outcome of whether the married man's wife work.
 
-The data collected from the experiment can be introduced through summary statistics.
+Before manipulating the data into graphs and tables to test these claims, we can first understand the cleaned data better with summary statistics.
 
@@
 
-As seen in @tbl-summ above, there are less than 500 data points present after removing single men as well as any empty data points used in the making of the summary statistics, contrary to the claims of Bursztyn et.al.
-```{r}
-
-```
+As seen in @tbl-summ above, there are less than 500 data points present in the cleaned data. From these data points, we can test
 
@@
 #| fig-cap: Density Histogram of Percentage Wedge
-cleaned_data <- wwoh_data |>
+histogram <- wwoh_data |>
   mutate(percentage_wedge = outside_wedge/30*100)
 
-p <- ggplot(cleaned_data, aes(x = percentage_wedge)) + 
+p <- ggplot(histogram, aes(x = percentage_wedge)) + 
   geom_histogram(aes(y = after_stat(density)), binwidth = 8, fill = "green", alpha = 0.6, color = "black") + 

### 2024-02-14 scripts/01-data_cleaning.R

@@ -13,15 +13,16 @@ library(dplyr)
 library(haven)
 
 #### Clean data ####
-raw_data <- read_dta("data/raw_data/01_main_exp_clean.dta")
+mainexp_raw_data <- read_dta("data/raw_data/01_main_exp_clean.dta")
+online_raw_data <- read_dta("data/raw_data/03_1st_online_svy_clean.dta")
 
 #taking out NA data from age variable as well as single men in the survey.
-cleaned_data <- raw_data |> clean_names() |> na.omit(age)|> mutate(
+main_cleaned <- raw_data |> clean_names() |> na.omit(age)|> mutate(
   age_groups = case_when(
   age <= 23 ~ 1,
   age >= 30 ~ 3,
   TRUE ~ 2)) |> filter(married == 1)
 
-
+online_cleaned
 #### Save data ####
 write_csv(cleaned_data, "data/analysis_data/cleaned_data.csv")

### 2024-02-15 paper/paper.qmd
Added and cleaned a new data set for follow up to the main experiment.

@@
     file = here("data/analysis_data/online_cleaned.csv"))
-wwoh_data <-
+main_cleaned <-
   read_csv(
@@
 ## Measurement and collection
-The "1st Online Survey Clean" will only be used to conduct analysis on the support of married Saudi Arabian men on women working outside of home.
+"1st Online Survey Clean" will only be used to conduct analysis on the support of married Saudi Arabian men on women working outside of home.
 Therefore, its selection process is not extremely extensive.
@@
 #| tbl-cap: Sample of Cleaned Main Experiment Data of Saudi Arabian Men on WWOH
-wwoh_data |> slice(1:5) |> kable()
+main_cleaned |> slice(1:5) |> kable()
 
@@
 
-Before manipulating the data into graphs and tables to test these claims, we can first understand the cleaned data better with summary statistics.
+The first claim can be easily explored using the cleaned national online survey data with its variable on the participant's support of WWOH.
+
+```{r}
+#| echo: false
+#| label: fig-wwoh
+#| fig-cap: Support of Young Married Men in Saudi Arabia of WWOH
+online_cleaned |> 
+  ggplot(aes(x = c_outside_self)) +
+  geom_bar() +
+  theme_minimal() +
+  labs(x = "Support of WWOH (Y = 1/N = 0)", y = "Frequency of Responses" )
+
+```
+@fig-wwoh confirms that the majority of young married men in Saudi Arabia do support women working outside of home.
+Out of the 728 observations, around 600 chose in favour that "In my opinion, women should be allowed to work outside of the home" @paper.
+This signifies that the first claim is accurate.
+
+Starting from the second claim, we will be using the main experiment data. Before manipulating it into graphs and tables, we can first understand the cleaned data better with summary statistics.
 
@@
 #| tbl-cap: Summary Statistics on Men Who Participated in the Main Experiment
-summary_stats <- wwoh_data |>
+summary_stats <- main_cleaned |>
   group_by(condition2) |>
@@
 
-summary_all <- wwoh_data |>
+summary_all <- main_cleaned |>
   summarize(
@@
 
-As seen in @tbl-summ above, there are less than 500 data points present in the cleaned data. From these data points, we can test
+As seen in @tbl-summ above, there are less than 500 data points present in the cleaned data.
+From these data points, we can test the claim that married men massively underestimate the level of support from other men in their communities.
+The surveys from the main experiment asked the participants about their predictions of how many others in the group of 30 (from 0 to 29) of many they know of, would support WWOH.
+The percentage difference between their beliefs and the actual calculated number is shown as wedges in @fig-time.
+This graph shows the distribution of the difference between beliefs on what percentage people support WWOH and actual percentage of people that support WWOH.
+The values were calculated as (participants guess about percent of session participants that agree with WWOH - the actual percentage of participants that agree with WWOH).
 
@@
 #| fig-cap: Density Histogram of Percentage Wedge
-histogram <- wwoh_data |>
+histogram <- main_cleaned |>
   mutate(percentage_wedge = outside_wedge/30*100)
@@
        x = "Percentage Wedge Value",
-       y = "Density",
-       caption = "Distribution of the difference between beliefs on what percentage people support WWOH and actual percentage of people that support WWOH.
-The values were calculated as (participants guess about percent of session participants that agree with WWOH - the actual percentage of participants that agree with WWOH") +
+       y = "Density") + 
   theme_minimal() +
@@
 ```
-In @fig-time, we plotted the “wedge” between the participant’s belief in what percentage of others would support WWOH and how many participants actually supported WWOH.
-In assessing the distribution of these wedges throughout all sessions, the data revealed that a substantial majority (72%) of the participants consistently undervalue the level of endorsement for WWOH within their session cohorts.
+In @fig-time, from assessing the distribution of these wedges throughout all sessions, the data revealed that a substantial majority (72%) of the participants consistently undervalue the level of endorsement for WWOH within their session cohorts.
 On average, this wedge is observed to be a 24 percentage points difference, aligning very similarly with the conclusions drawn from the original paper @paper.
+Thus, the second claim of that married men massively underestimate the level of support from other men in their communities is further substantiated.
 
@@
 
-# Additional data details
-
-## Posterior predictive check
-
 ## Diagnostics

### 2024-02-15 scripts/01-data_cleaning.R

@@ -14,15 +14,28 @@ library(haven)
 
 #### Clean data ####
 mainexp_raw_data <- read_dta("data/raw_data/01_main_exp_clean.dta")
+follow_raw_data <- read_dta("data/raw_data/02_follow_up_clean.dta")
 online_raw_data <- read_dta("data/raw_data/03_1st_online_svy_clean.dta")
+sec_raw_data <- read_dta("data/raw_data/04_2nd_online_svy_clean.dta")
 
 #taking out NA data from age variable as well as single men in the survey.
-main_cleaned <- raw_data |> clean_names() |> na.omit(age)|> mutate(
+main_cleaned <- mainexp_raw_data |> clean_names() |> 
+  na.omit(age)|> mutate(
   age_groups = case_when(
   age <= 23 ~ 1,
   age >= 30 ~ 3,
   TRUE ~ 2)) |> filter(married == 1)
 
-online_cleaned
+follow_cleaned <- follow_raw_data |> clean_names() |> 
+  na.omit(age) |>
+  select(employed_3mos_out_fl, employed_now_out_fl) |> na.omit() 
+
+online_cleaned <- online_raw_data |> clean_names() |> 
+  select(c_outside_self)|>
+  na.omit()
+
 #### Save data ####
-write_csv(cleaned_data, "data/analysis_data/cleaned_data.csv")
+write_csv(main_cleaned, "data/analysis_data/main_cleaned.csv")
+write_csv(follow_cleaned, "data/analysis_data/follow_cleaned.csv")
+write_csv(online_cleaned, "data/analysis_data/online_cleaned.csv")
+

### 2024-02-15 scripts/01-data_cleaning.R
Pushing through cleaned data of second survey.

@@ -34,8 +34,11 @@ online_cleaned <- online_raw_data |> clean_names() |>
   select(c_outside_self)|>
   na.omit()
 
+sec_cleaned <- sec_raw_data |> clean_names() |>
+  select(discuss_freq) |> na.omit() 
+
 #### Save data ####
 write_csv(main_cleaned, "data/analysis_data/main_cleaned.csv")
 write_csv(follow_cleaned, "data/analysis_data/follow_cleaned.csv")
 write_csv(online_cleaned, "data/analysis_data/online_cleaned.csv")
-
+write_csv(sec_cleaned, "data/analysis_data/sec_cleaned.csv")

### 2024-02-15 paper/paper.qmd
Finished replication of three graphs/tables.

@@
     file = here("data/analysis_data/main_cleaned.csv"))
+follow_cleaned <-
+  read_csv(
+    file = here("data/analysis_data/follow_cleaned.csv"))
+sec_cleaned <-
+   read_csv(
+    file = here("data/analysis_data/sec_cleaned.csv"))
 
@@
 
-The first data used in this analysis - "1st Online Survey Clean" - is sourced from the replication package provided by Bursztyn et.al (2020).
-The data was collected by the researchers in the original paper through an online survey with a treatment group and a control group.
-This imported data contains 1460 observations and 21 variables.
-
-The second data used in this analysis - "Main Experiment Clean" - is also sourced from the replication package provided by Bursztyn et.al (2020).
-The data was collected by the researchers in the original paper through a more selective filtering process with an experiment conducted in-person with a treatment group and a control group.
-This data contains 500 observations and 36 variables.
+There are four data sets used in this paper. 1. "1st Online Survey Clean",  2. "2nd Online Survy Clean", 3. "Main Experiment Clean", and  4. "Follow Up Clean".
+The all four data sets are sourced from the replication package provided by Bursztyn et.al (2020) as they collected all the data in their research.
+The collection processes will be further explained in the following subsection.
 
@@
 This survey was conducted nationally and anonymously.
-The other aspects of this survey is not further discussed as the data will not be used in this paper.
+This imported data contains 1460 observations and 21 variables.
+However, the other aspects of this survey is not further discussed as the data will not be used in this paper.
 
-However, the main experiment data needs a more extensive examination.
+Another data set used in our paper is the “Second Online Survey.” This survey was very similar to the first, targeted towards married men in Saudi Arabia.
+The survey contained 703 participants, all of whom were married 18-45 year olds and 20 variables.
+The researchers decided to increase the upper-bound in the hopes of reaching a larger sample.
+The survey was conducted from January to February 2020 and participants responded anonymously online.
+From this data set, the only relevant variable for our analysis will be the “discuss_freq” variable, which indicates how often married men talk about WWOH with their friends and colleagues.
+
+However, the main experiment data "Main Experiment Clean" needs a more extensive examination.
 The sampling for the experiment was conducted through a partnership between a local branch of an international survey company and Bursztyn et.al.
@@
 The cleaned data will be further explored in @sec-explore.
+
+Lastly, the data set "Follow Up Clean" is information from the follow up survey that was conducted on the same sample as the main experiment three months alter.
+This survey is a phone call and the variables that will be used is to examine the change in the participants' wifes' employment since the main experiment.
+This data set contains 500 observations and 33 variables.
 

### 2024-02-15 scripts/99-replications.R

@@ -1,19 +1,82 @@
 #### Preamble ####
-# Purpose: Replicated graphs from... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Replication of three graphs in original paper.
+# Author: Tracy Yang, Alex Sun
+# Date: 12 February 2024
+# Contact: ycart.yang@mail.utoronto.ca; boyalexsun@gmail.com
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
-
+# Pre-requisites: 01-data_cleaning.R
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
 
 #### Load data ####
-# [...ADD CODE HERE...]
+main_cleaned <-
+  read_csv(
+    file = here("data/analysis_data/main_cleaned.csv"))
+sec_cleaned <-
+  read_csv(
+    file = here("data/analysis_data/sec_cleaned.csv"))
 
 
+#### Replication of Table 2 Summary Statistics Table ####
+#| echo: false
+#| label: tbl-summ
+#| tbl-cap: Summary Statistics on Men Who Participated in the Main Experiment
+summary_stats <- main_cleaned |>
+  group_by(condition2) |>
+  summarize(
+    Observations = n(),
+    Age = mean(age, na.rm =TRUE),
+    Children = mean(children, na.rm = TRUE),
+    "College(%" = sum(college_deg, na.rm = TRUE)/n()*100,
+    "Employed(%)" = sum(employed_now, na.rm = TRUE)/n()*100,
+  ) |>
+  bind_rows()|>
+  mutate(group = c("Control", "Treatment"))
+
+summary_stats |> kable()
+
+summary_all <- main_cleaned |>
+  summarize(
+    Total = n(),
+    Age = mean(age, na.rm =TRUE),
+    Children = mean(children, na.rm = TRUE),
+    "College" = sum(college_deg, na.rm = TRUE)/n()*100,
+    "Employed(%)" = sum(employed_now, na.rm = TRUE)/n()*100)
+
+summary_all |> kable()
+
+#### Replication of Figure 2 Wedges in Perceptions of Others’ Beliefs: Main Experiment ####
+#| echo: false
+#| label: fig-time
[…]

### 2024-02-15 paper/paper.qmd
Added more tables, graphs, citations.

@@
 #install.packages("knitr")
+#install.packages("kableExtra")
+#install.packages("webshot")
 
@@
 #| fig-cap: Support of Young Married Men in Saudi Arabia of WWOH
+
 online_cleaned |> 
@@
 #| label: fig-time
-#| fig-cap: Density Histogram of Percentage Wedge
+#| fig-cap: Density Histogram of Percentage Wedge on Difference Between Beliefs and Actual Calculation
 histogram <- main_cleaned |>
@@
   scale_x_continuous(limits = c(-100, 100))
+print(p)
 
-print(p)
 ```
+
 In @fig-time, from assessing the distribution of these wedges throughout all sessions, the data revealed that a substantial majority (72%) of the participants consistently undervalue the level of endorsement for WWOH within their session cohorts.
@@
 
+The last claim this replication paper is going to focus on is that correcting beliefs about others' feelings will affect the outcome of whether the married man's wife works.
+In the main experiment done by Bursztyn et.al, a follow up survey three months later records the difference in the participant's wife's employment difference @paper.
+As the men experienced learning about others' surprisingly supportive views on WWOH during the first survey, this three-month difference in wifes' employments maybe attributed to the correcting of beliefs.
+The difference is shown in  below.
+
+```{r}
+#| echo: false
+#| label: tbl-empl
+#| tbl-cap: Employment Difference of Wives between Two Surveys Three Months Apart
+#| tbl-subcap: ["Treatment", "Control"]
+#| layout-ncol: 2
+
+follow_cleaned |> filter(condition2==1) |>
+  count(emply_prev, emply_now) |> kable()
+
+follow_cleaned |> filter(condition2==0) |>
+  count(emply_prev, emply_now) |> kable()
+
+```
+As seen in @tbl-empl, there are slight differences between the treatment and control group in terms of the participants' wives employment since the first survey.
+
 # Discussion {#sec-discussion}
 
-## First discussion point {#sec-first-point}
+```{r}
+#| echo: false
+#| label: fig-diss
+#| fig-cap: Frequency of WWOH Discussions for Participants in Survey
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
+chart <- sec_cleaned |>
+  mutate(freq = case_when(
+    discuss_freq == 1 ~ "Very Often",
+    discuss_freq == 2 ~ "Often",
+    discuss_freq == 3 ~ "Sometimes",
+    discuss_freq == 4 ~ "Rarely",
+    discuss_freq == 5 ~ "Very Rarely"))
 
-## Second discussion point
+chart |>
+  ggplot(mapping = aes(x = freq)) +
+  geom_bar() +
+  theme_minimal() +
+  labs(x = "Age group", y = "Number of observations")
 
-## Third discussion point
+```
 
@@
 
-\appendix
-
-# Appendix {-}
-
-## Diagnostics
-
 \newpage

### 2024-02-15 scripts/01-data_cleaning.R

@@ -28,7 +28,9 @@ main_cleaned <- mainexp_raw_data |> clean_names() |>
 
 follow_cleaned <- follow_raw_data |> clean_names() |> 
   na.omit(age) |>
-  select(employed_3mos_out_fl, employed_now_out_fl) |> na.omit() 
+  select(employed_3mos_out_fl, employed_now_out_fl, condition2) |> na.omit() |>
+  rename(emply_prev = employed_3mos_out_fl) |>
+  rename(emply_now = employed_now_out_fl)
 
 online_cleaned <- online_raw_data |> clean_names() |> 
   select(c_outside_self)|>

### 2024-02-15 paper/paper.qmd
Deleted unwanted data from the main experiment data set and created new graphs.

@@
 ---
-title: "The Analysis of Pluralistic Ignorance of Married Men in Saudi Arabia on Women Working Outside of Home (WWOH) ^[Code and data are available at: https://github.com/YcartXin/Analysis-of-Men-in-Saudi-Arabia-on-WWOH]"
+title: "The Analysis of Pluralistic Ignorance of Married Men in Saudi Arabia on Women Working Outside of Home (WWOH) ^[Code and data are available at: https://github.com/YcartXin/Analysis-of-Men-in-Saudi-Arabia-on-WWOH; Reproduction DOI: https://doi.org/10.48152/ssrp-1wa4-dk30]"
 author: 
@@
 Lastly, the data set "Follow Up Clean" is information from the follow up survey that was conducted on the same sample as the main experiment three months alter.
-This survey is a phone call and the variables that will be used is to examine the change in the participants' wifes' employment since the main experiment.
+This survey is a phone call and the variables that will be used is to examine the change in the participants' wifes' employment since the main experiment as well as whether the husband was in the treatment or control group.
 This data set contains 500 observations and 33 variables.
@@
 The online survey data now consists of only one variable with 728 observations.
-The variable signifies whether the respondent supports women working outside of home.
-
-@tbl-sampleonline shows what the online national survey data looks like after cleaning.
-
-```{r}
-#| echo: false
-#| label: tbl-sampleonline
-#| tbl-cap: Sample of Cleaned Online National Survey Data of Saudi Arabian Men on WWOH
-online_cleaned |> slice(1:5) |> kable()
-
-```
+The variable "c_outside_self" signifies whether the respondent supports women working outside of home.
+The follow up data now consists of 361 observations with three variables: "emply_prev", "emply_now", "condition2".
+The second main experiment data includes 702 observations and 1 variable as well, which is the frequency of discussion of WWOH issues.
 
@@
 # Results {#sec-results}
-This section will first affirm the findings in the original paper with the cleaned data. As stated in @sec-intro, the three main claims made by Bursztyn et.al are:
+
+## Aanalysing origial paper
+This section will try to affirm the findings in the original paper with the cleaned data. As stated in @sec-intro, the three main claims made by Bursztyn et.al are:
 + The vast majority of married men in Saudi Arabia privately support WWOH.
@@
 
-Starting from the second claim, we will be using the main experiment data. Before manipulating it into graphs and tables, we can first understand the cleaned data better with summary statistics.
+Starting from the second claim, we will be using the main experiment data.
+Before manipulating it into graphs and tables, we can first understand the cleaned data better with summary statistics.
+The "condition2" variable separates the treatment and control groups.
 
@@
 As the men experienced learning about others' surprisingly supportive views on WWOH during the first survey, this three-month difference in wifes' employments maybe attributed to the correcting of beliefs.
-The difference is shown in  below.
+The difference is shown in @tbl-empl below.
 
@@
 ```
-As seen in @tbl-empl, there are slight differences between the treatment and control group in terms of the participants' wives employment since the first survey.
+As seen in @tbl-empl, there are slight differences between the treatment and control groups in terms of the participants' wives employment since the first survey.
+The number of women who moved from not working three months ago to now working is four in the treatment group while only 1 in the control group.
+The number of women who were employed but is not now is 4 is the treatment group and 3 in the control group.
+Due to the limited data size of around 350 and the insignificant differences in the changes in employment between the treatment and control group, this @tbl-empl cannot be decisive evidence in supporting correcting beliefs about others' feelings will affect the outcome of whether the married man's wife works.
+However, the tables fall more in favour of agreeing than disagreeing.
+
+## Further Analysis
+In this section, the analysis will branch off from the original paper and explore the demographics of the men who support/oppose women working outside of home.
+We will first consider education as a factor that may determine support for WWOH.
+Research shows that one additional year of education reduces the probability of agreeing with women's traditional gender role @educ.
+This relationship in the existing data is explored in XX.
+
+```{r}
+#| echo: false
+#| label: fig-educ
+#| fig-cap: Graph on the impact of education on supporting WWOH
+
+main_cleaned <- mainexp_raw_data |> clean_names() |> 
+  na.omit(age)|> mutate(
+  age_groups = case_when(
+  age <= 23 ~ 1,
+  age >= 30 ~ 3,
+  TRUE ~ 2)) |> filter(married == 1)
+
+eduimpact <- main_cleaned |> mutate(support = ifelse(
+  outside_self == 1, "support", "oppose")) |>
+  mutate(edu_words = case_when(
+
+  ))
+
+eduimpact |>
+  ggplot(mapping = aes(x = education, fill = support)) +
+  geom_bar() +
+  labs(x = "Age group", y = "Number of observations", fill = "Vote") +
+  theme(legend.position = "bottom")
+
+```
 

### 2024-02-15 scripts/01-data_cleaning.R

@@ -19,12 +19,15 @@ online_raw_data <- read_dta("data/raw_data/03_1st_online_svy_clean.dta")
 sec_raw_data <- read_dta("data/raw_data/04_2nd_online_svy_clean.dta")
 
 #taking out NA data from age variable as well as single men in the survey.
-main_cleaned <- mainexp_raw_data |> clean_names() |> 
-  na.omit(age)|> mutate(
+main_cleaned <- mainexp_raw_data |> clean_names() |> filter(married == 1) |>
+  mutate(
   age_groups = case_when(
   age <= 23 ~ 1,
   age >= 30 ~ 3,
-  TRUE ~ 2)) |> filter(married == 1)
+  TRUE ~ 2)) |> select(
+    age, education, outside_self, condition2, employed_now, college_deg,
+                    children, outside_wedge, age_groups) |> na.omit()
+  
 
 follow_cleaned <- follow_raw_data |> clean_names() |> 
   na.omit(age) |>

### 2024-02-15 paper/paper.qmd
Added more graphs.

@@
 Research shows that one additional year of education reduces the probability of agreeing with women's traditional gender role @educ.
-This relationship in the existing data is explored in XX.
+This relationship in the existing data is explored in @fig-educ.
 
@@
 #| label: fig-educ
-#| fig-cap: Graph on the impact of education on supporting WWOH
-
-main_cleaned <- mainexp_raw_data |> clean_names() |> 
-  na.omit(age)|> mutate(
-  age_groups = case_when(
-  age <= 23 ~ 1,
-  age >= 30 ~ 3,
-  TRUE ~ 2)) |> filter(married == 1)
+#| fig-cap: Graphs on the Impact that Different levels of Education has on Supporting WWOH
+#| fig-subcap: ["Education Levels", "With/Without College Degree"]
+#| layout-nrows: 2
 
@@
   outside_self == 1, "support", "oppose")) |>
-  mutate(edu_words = case_when(
+  mutate(degree = case_when(
+  college_deg == 0 ~ "No Degree",
+  college_deg == 1 ~ "Degree"))
 
-  ))
+eduimpact <- eduimpact |> mutate(edul = case_when(
+  education == 3 ~ "Secondary",
+  education == 4 ~ "Middle",
+  education == 5 ~ "Diploma",
+  education == 6 ~ "Bachelor",
+  education == 7 ~ "Masters",
+  education == 8 ~ "Ph.D",
+  TRUE ~ "Post Graduate"))
 
 eduimpact |>
-  ggplot(mapping = aes(x = education, fill = support)) +
+  ggplot(mapping = aes(x = fct_inorder(edul), fill = support)) +
   geom_bar() +
-  labs(x = "Age group", y = "Number of observations", fill = "Vote") +
+  labs(x = "Education Level", y = "Number of observations", fill = "Stance") +
+  theme(legend.position = "bottom")
+
+eduimpact |>
+  ggplot(mapping = aes(x = fct_inorder(degree), fill = support)) +
+  geom_bar() +
+  labs(x = "Education Level", y = "Number of observations", fill = "Stance") +
   theme(legend.position = "bottom")
@@
 ```
+According to @fig-educ, the number of people that oppose women working outside of home do decrease with education as Diploma has one of the highest ratio of those that oppose.
+However, the ratio for Ph.D, and Post graduate are not obvious due to their significantly smaller number of participants.
+The next graph combines the participants into two bigger groups for better comparison.
+In with/without college degree graph, the men are separated into having/not having obtained a college degree as college is a big step in education that can differentiate people's views.
+From fig-educ, it is clear that most of the opposing participants have a Bachelor degree with the fewest having a Ph.D or Post Graduate Degree.
+This is due to having a bachelor degree is the most frequent in the population and does not indicate any correlation.
+
+This paper will further look at the demographics of age and how it affects the participants' stance on WWOH. 
+```{r}
+#| echo: false
+#| label: fig-age
+#| fig-cap: Graph on the Distribution of Age on the Stance of WWOH
+
+ageimpact <- main_cleaned |> mutate(support = ifelse(
+  outside_self == 1, "support", "oppose")) |>
+  mutate(age_bracket = case_when(
+  age <= 23 ~ "18 - 23",
+  age >= 30 ~ "30 - 35",
+  TRUE ~ "24 - 30"))
+
+ageimpact |>
+  ggplot(mapping = aes(x = age_bracket, fill = support)) +
+  geom_bar() +
+  labs(x = "Age Groups", y = "Number of observations", fill = "Stance") +
+  theme(legend.position = "bottom")
+
+```
+From @fig-age, there is a surprising trending of decreasing opposers of WWOH as Saudi Arabian men grew older.
 

### 2024-02-15 paper/paper.qmd
Some edits

@@
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "This study replicates and expands upon the seminal work of Bursztyn, Gonzalez, and Yanagizawa-Drott to explore attitudes toward women working outside the home (WWOH) among young married men in Saudi Arabia.
+Our findings confirm that a significant majority of this demographic privately endorses WWOH while concurrently underestimating the extent of support among their peers.
+When participants' misconceptions were corrected, there was a notable increase in their willingness to assist their wives in job searching, a behavior that incurs personal cost.
+Furthermore, we investigated how varying demographics affected support values.
+We propose that future research should focus on the dissemination of information regarding gender norms and the role of social networks in shaping labor market behaviors.
+This could pave the way for policy interventions aimed at reducing gender disparities in the workforce and fostering a more accurate reflection of societal values."
 format: 
@@
 
-For the cleaned main experiment data, irrelevant variables and empty responses were also deleted. It now consists of XX observations with XX variables. 
+For the cleaned main experiment data, irrelevant variables and empty responses were also deleted. It now consists of 482 observations with 8 variables. 
 The variables are listed and explained below:
+
++ age
++ education which has five different categories: Secondary, Middle, Diploma, Bachelor, Masters, Ph.D, and Post Graduates
++ outside_self refers to whether the participant supports WWOH [0,1]
++ condition2 signifies treatment group when 1 and control group when 0
++ employed_now records whether the participant is currently employed
++ college_deg is another dummy variable referring to whether the participant has a college degree
++ children refers to how many children the participant and his wife has
++ outside_wedge is the difference in the belief between how many people in the group of 30 the participant believes would support WWOH and the actual number
 
@@
 ```
-From @fig-age, there is a surprising trending of decreasing opposers of WWOH as Saudi Arabian men grew older.
+From @fig-age, there is an interesting trending of decreasing opposers of WWOH as Saudi Arabian men grew older.
+The age group of 18 to 23 has the smallest propotion of WWOH supporters.
+However, it is difficult to compare the 30 to 35 age group as its sample size is much smaller.
+Nonetheless, younger man may be more opposed to WWOH as older men have a more stablized home with children to take care of.
 
 # Discussion {#sec-discussion}
+
+## Findings
+In this paper, we replicated the results of Bursztyn, Gonzalez, and Yanagizawa-Drott.
+The paper sought to assert that majority of married Saudi Arabian men support women working outside the home.
+From the data, we have replicated the following major findings:
+The vast majority of married Saudi Arabian men support WWOH
+Married men vastly underestimate the level of support from other married men
+Correcting these beliefs about others’ feelings will affect the outcome of whether the married man’s wife works.
+
+	The original experiment discovered that nearly all participants significantly underestimated the overall support of WWOH.
+The survey data showed that while 83% of the participants are in favour of WWOH, the average perception is that only 56% are in favour; 82% of participants underestimated the support for WWOH.
+
+## Bias & Weaknesses
+The design of this experiment may illicit response bias from participants.
+Within the lens of this progressive social study, the fact that participants responded to the surveys anonymously online may sway some of them to answer in ways that differed from their true beliefs.
+The study addresses potential limitations regarding such bias by implementing a list experiment to mitigate these concerns (Fisher, 1993).
+The list experiment composed of giving participants a list of topics and they were told to state how many they agreed with, but not indicate which ones those were.
+This method is known to reduce the effects of social desirability bias.
+Despite anonymity, concerns remained that participants might feel pressured to respond in socially acceptable ways.
+If true, the bias would have an impact on our estimand, altering the values found and depicted in @fig-time.
+The list experiment, providing plausible deniability, showed consistent support for women working outside the home, suggesting minimal bias impact.
+Additionally, comparison with the Arab Barometer's findings corroborated the study's external validity, indicating a long-standing high level of support for women working outside the home among Saudi men, thereby strengthening the study's reliability despite potential limitations.
+
+## Main Motivator Behind the Wedge Discrepancy
+
+The study consistently illustrates the impact of misperceived social norms on labor market decisions, specifically in the context of Saudi Arabia, where a significant gap between actual and perceived support for women working outside the home is observed.
+The underestimation of societal support for women's employment reflects deeper issues of communication within society.
+Speculatively, this misperception may stem from insufficient individual-to-individual communication, possibly exacerbated by mass media failing to accurately represent societal values.
+Further investigation into the role of communication reveals that personal connections influence perception accuracy.
 
@@
 
-## Weaknesses and next steps
+An additional online survey aimed to delve deeper into these communication dynamics, highlights the fact that discussions about women working outside the home among male friends and relatives are infrequent.
+This lack of discourse correlates with larger gaps in perception versus reality, suggesting that minimal conversation contributes to widespread misperceptions.
+This correlation might also suggest a reverse causality, where the anticipation of conservative backlash inhibits open discussions, perpetuating a cycle of pluralistic ignorance.
+The lack of communication may not be entirely mass media’s failure to properly portray societal beliefs.
+When questioned, nearly 38% of participants very rarely discuss WWOH among their male friend circles.
+As shown in Figure _, the topic of WWOH is not very readily discussed among peers and colleagues.
+We hypothesize that this behaviour will extend onto social media, further supporting the idea that the perceived lack of support for WWOH is exacerbated by simply a deficiency in attention.
 
-Weaknesses and next steps should also be included.
+## Demographic
+
+## Future Research
+The study suggests several directions for future research, emphasizing the transformative potential of information dissemination on societal norms and labor market behaviors, particularly regarding female employment in Saudi Arabia and possibly beyond.
+It proposes expanding research to understand how information about gender norms spreads within social networks and its broader impacts.
+Additionally, it highlights the need to explore women's perspectives on labor participation, given their high reported support for working outside the home.
+Understanding the stigma against women's employment and the motivations behind male guardians' attitudes offers another fruitful avenue for developing targeted policy interventions.
+This research could contribute to strategies that more effectively address gender disparities in the workforce.
 
 \newpage
-
-\newpage

### 2024-02-15 scripts/01-data_cleaning.R

@@ -20,14 +20,8 @@ sec_raw_data <- read_dta("data/raw_data/04_2nd_online_svy_clean.dta")
 
 #taking out NA data from age variable as well as single men in the survey.
 main_cleaned <- mainexp_raw_data |> clean_names() |> filter(married == 1) |>
-  mutate(
-  age_groups = case_when(
-  age <= 23 ~ 1,
-  age >= 30 ~ 3,
-  TRUE ~ 2)) |> select(
-    age, education, outside_self, condition2, employed_now, college_deg,
-                    children, outside_wedge, age_groups) |> na.omit()
-  
+   select(age, education, outside_self, condition2, employed_now, college_deg,
+                    children, outside_wedge) |> na.omit()
 
 follow_cleaned <- follow_raw_data |> clean_names() |> 
   na.omit(age) |>

### 2024-02-15 scripts/02-test_data.R
Finished writing the tests for the cleaned data.

@@ -1,15 +1,53 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Cleans the downloaded Saudi Arabia survey data for married men on giving consent to wife working outside of home.
+# Author: Tracy Yang, Alex Sun
+# Date: 12 February 2024
+# Contact: ycart.yang@mail.utoronto.ca; boyalexsun@gmail.com
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: None
 
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
 
-#### Test data ####
+#### Importing  ####
+online_cleaned <-
+  read_csv(
+    file = here("data/analysis_data/online_cleaned.csv"))
+main_cleaned <-
+  read_csv(
+    file = here("data/analysis_data/main_cleaned.csv"))
+follow_cleaned <-
+  read_csv(
+    file = here("data/analysis_data/follow_cleaned.csv"))
+sec_cleaned <-
+  read_csv(
+    file = here("data/analysis_data/sec_cleaned.csv"))\
+
+#### Testing Data ####
+## Online Cleaned Tests ##
+online_cleaned$c_outside_self |> unique() |> length() == 2
+online_cleaned$c_outside_self |> max() == 1
+online_cleaned$c_outside_self |> min() == 0
+
+# Main Cleaned Tests ##
+
+main_cleaned$education |> max() == 9
+main_cleaned$education |> min() == 3
+main_cleaned$age |> min() == 18
+main_cleaned$outside_self |> unique() == 2
+main_cleaned$condition2 |> unique() == 2
+main_cleaned$college_deg |> class() == "numeric"
+main_cleaned$employed_now |> min() == 0
+main_cleaned$outside_wedge |> min() == -29
+
+# Follow-up tests
+follow_cleaned$emply_prev |> unique() == 2
+follow_cleaned$emply_now |> unique() == 2
+follow_cleaned$condition2 |> unique() == 2
+follow_cleaned$condition2 |> class() == "numeric"
+
+# Online survey tests
[…]

### 2024-02-15 paper/paper.qmd
One more commit with final touches

@@
 
-Pluralistic ignorance describes the misalignment between private and public beliefs XX.
+Pluralistic ignorance describes the misalignment between private and public beliefs @pluralistic.
 In the context of the paper by Bursztyn et.al.
@@
 Even though the data imported has already been cleaned, it is not in the state that can be directly used in this paper.
-The cleaning process will keep XX as they are relevant to replicate the targeted aspects and the following analysis.
+The cleaning process will keep 7 as they are relevant to replicate the targeted aspects and the following analysis.
 Additionally, the main experiment's raw data's sampling methodology also contains flaws.
@@
 
-For the cleaned main experiment data, irrelevant variables and empty responses were also deleted. It now consists of 482 observations with 8 variables. 
+For the cleaned main experiment data, irrelevant variables and empty responses were also deleted. It now consists of 482 observations with 7 variables. 
 The variables are listed and explained below:
@@
 + college_deg is another dummy variable referring to whether the participant has a college degree
-+ children refers to how many children the participant and his wife has
 + outside_wedge is the difference in the belief between how many people in the group of 30 the participant believes would support WWOH and the actual number
@@
     Age = mean(age, na.rm =TRUE),
-    Children = mean(children, na.rm = TRUE),
     "College(%" = sum(college_deg, na.rm = TRUE)/n()*100,
@@
     Age = mean(age, na.rm =TRUE),
-    Children = mean(children, na.rm = TRUE),
     "College" = sum(college_deg, na.rm = TRUE)/n()*100,
@@
 The original experiment discovered that nearly all participants significantly underestimated the overall support of WWOH.
-The survey data showed that while 83% of the participants are in favour of WWOH, the average perception is that only 56% are in favour; 82% of participants underestimated the support for WWOH.
+The survey data showed that while 83% of the participants are in favour of WWOH, the average perception is that only 56% are in favour; 82% of participants underestimated the support for WWOH @paper.
 
@@
 Within the lens of this progressive social study, the fact that participants responded to the surveys anonymously online may sway some of them to answer in ways that differed from their true beliefs.
-The study addresses potential limitations regarding such bias by implementing a list experiment to mitigate these concerns (Fisher, 1993).
+The study addresses potential limitations regarding such bias by implementing a list experiment to mitigate these concerns.
 The list experiment composed of giving participants a list of topics and they were told to state how many they agreed with, but not indicate which ones those were.
@@
 The list experiment, providing plausible deniability, showed consistent support for women working outside the home, suggesting minimal bias impact.
-Additionally, comparison with the Arab Barometer's findings corroborated the study's external validity, indicating a long-standing high level of support for women working outside the home among Saudi men, thereby strengthening the study's reliability despite potential limitations.
+Additionally, comparison with the Arab Barometer's findings corroborated the study's external validity, indicating a long-standing high level of support for women working outside the home among Saudi men, thereby strengthening the study's reliability despite potential limitations @specia.
 
@@
 This lack of discourse correlates with larger gaps in perception versus reality, suggesting that minimal conversation contributes to widespread misperceptions.
-This correlation might also suggest a reverse causality, where the anticipation of conservative backlash inhibits open discussions, perpetuating a cycle of pluralistic ignorance.
+This correlation might also suggest a reverse causality, where the anticipation of conservative backlash inhibits open discussions, perpetuating a cycle of pluralistic ignorance @pluralistic.
 The lack of communication may not be entirely mass media’s failure to properly portray societal beliefs.
 When questioned, nearly 38% of participants very rarely discuss WWOH among their male friend circles.
-As shown in Figure _, the topic of WWOH is not very readily discussed among peers and colleagues.
+As shown in @fig-diss, the topic of WWOH is not very readily discussed among peers and colleagues.
 We hypothesize that this behaviour will extend onto social media, further supporting the idea that the perceived lack of support for WWOH is exacerbated by simply a deficiency in attention.
 
-## Demographic
+## Demographics
+Straying from Burzstyn, Gonzalez, and Yanagizawa-Drott’s original analysis, we delve further into how demographical differences may or may not affect participants’ support for WWOH.
+We hypothesized that higher levels of education may correlate with increased rates of WWOH support.
+As shown in Figure 3 a and b,  there is a noticeable increase in percentage of individuals who oppose WWOH among Bachelor degree’s.
+However, this may be attributed to the lesser number of participant’s at any other education level.
+Overall, although there is a noticeable difference, the lack of participants at higher education levels makes it difficult to draw any significant conclusions about the correlation between education level and support for WWOH.
+We initially believed that higher levels of education may indicate more progressive beliefs due to increased likelihood of exposure to Western literature but more testing is required to draw any concrete results.
+
+When separated into age groups, it appears that 18-23 year olds have the highest rate of WWOH opposition.
+This was shocking as we expected the younger generation with more exposure to social media and international communication to have the lowest rate of WWOH opposition.
+From @fig-age, we see that as the age groups get larger, so does the proportional support for WWOH.
+Similarly to when we separated the participants by education, we run into the issue of varying numbers of participants for each bin.
+30-35 year old participants compose roughly a third of the number of 18-23 year olds making us skeptical about any conclusions drawn.
 
@@
 
+When we split the participants into separate demographics, we found surprising trends.
+Categories that we believed would be more progressive actually turned out to have the highest rate of WWOH opposition.
+However, as shown in Figures 3 and 4, there is a disproportionate number of participants in each bin.
+Especially for higher education levels, the minimal number of participants with higher levels of education make it difficult to draw any correlation between education level and WWOH support.
+An avenue for further research may be to stratify the research sample with a big enough number of participants so that a better correlation can be shown.
+
 \newpage

### 2024-02-15 scripts/02-test_data.R

@@ -31,7 +31,6 @@ online_cleaned$c_outside_self |> max() == 1
 online_cleaned$c_outside_self |> min() == 0
 
 # Main Cleaned Tests ##
-
 main_cleaned$education |> max() == 9
 main_cleaned$education |> min() == 3
 main_cleaned$age |> min() == 18
